\sysfull

### 2018-04-13 paper/evaluation.tex
table holder for apps evaluation

\begin{table}[t]
	\centering
	\footnotesize
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline
		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & 287 & $<$1\\
		dft$^\dagger$ & --- & --- & --- & --- & --- & --- & 222 & 293 & ---\\
		%dd &  &  &  &  &  &  &  & 287 &  \\
		\hline
	\end{tabular}
		\caption{Comparison between \sys and Alpaca benchmarks.}
		\label{table:compiler_result}\vspace{-0.5cm}
\end{table}

>>>>

\begin{table}
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		Application & \multicolumn{2}{| c |}{Memory footprint} & No. tasks & SLOC \\
		{} & \sys & Alpaca & {} & {} \\
		\hline\hline
		\textbf{ar} & --- & --- & --- & ---\\
		\hline
	\end{tabular}
		\caption{Comparison between \sys and Alpaca benchmarks.}
		\label{table:compiler_result}\vspace{-0.5cm}
\end{table}

%\begin{table}[t]
%	\centering
%	\renewcommand{\tabcolsep}{1pt}
%	\begin{tabular}{|l|cc|cc|cc|cc|c|}
%		\hline
%		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
%		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
%		\hline\hline
%		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
%		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
%		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
%		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
%		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
%		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & 287 & $<$1\\
%		dft$^\dagger$ & --- & --- & --- & --- & --- & --- & 222 & 293 & ---\\
%		%dd &  &  &  &  &  &  &  & 287 &  \\
%		\hline
%	\end{tabular}
%		\caption{Comparison between \sys and Alpaca benchmarks.}
%		\label{table:compiler_result}\vspace{-0.5cm}
%\end{table}
